Ideal model selection is impossible

### 2014-10-23 Facticity/Facticity/paper.tex
typo

We can now relate the complexity of $f$ under the two enumerations as follows:
\begin{align*}
K^\phi(f) &= \min\left\{ K^\phi(j) : \phi_j = f \right\}& \\
       &= \min\left\{ K^\phi(1^r0i) : \phi_{ri} = f \right\}& \\
       &\ge  \min\left\{ K^\phi(i) : \phi_{ri} = f \right\}-c'&\text{by~\eqref{eq:prelim1}}\\
       &\geq \min\left\{ K^\psi(i)  : \phi_{ri} = f \right\}+r+1-c'& \text{by \eqref{eq:prelim2}}\\
       &= \min\left\{ K^\psi(i) : \psi_{i} = f \right\} + r+1 -c'& \\
       &= K^\psi(f) + r + 1 - c'.
\end{align*}
The proof is completed by choosing $r=c+c'-1$.
\end{proof}

>>>>

We can now relate the complexity of $f$ under the two enumerations as follows:
\begin{align*}
K^\phi(f) &= \min\left\{ K^\phi(j) : \phi_j = f \right\}& \\
       &= \min\left\{ K^\phi(1^r0i) : \phi_{1^r0i} = f \right\}& \\
       &\ge  \min\left\{ K^\phi(i) : \phi_{1^r0i} = f \right\}-c'&\text{by~\eqref{eq:prelim1}}\\
       &\geq \min\left\{ K^\psi(i)  : \phi_{1^r0i} = f \right\}+r+1-c'& \text{by \eqref{eq:prelim2}}\\
       &= \min\left\{ K^\psi(i) : \psi_{i} = f \right\} + r+1 -c'& \\
       &= K^\psi(f) + r + 1 - c'.
\end{align*}
The proof is completed by choosing $r=c+c'-1$.
\end{proof}
